---
title: "Stryker Customer Intelligence Tutorial"
author: "Blake Tindol"
date: "8/8/2020"
output: html_document
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
setwd("C:/Users/blake/OneDrive/Stryker Project/Country Leaflet Information Dashboard")
options(scipen = 999)
if(!require("pacman")){
  install.packages("pacman")
}
pacman::p_load(dplyr, data.table,lubridate,zoo,riem,tidyr,countrycode,RCurl,stringr,tidyverse,shiny,miniUI,taskscheduleR,gtrendsR,tidycensus,sf,leaflet,mapview,viridis,tidyquant,tigris,tmap,sf,maps,tidycensus,xts,ggsflabel,scales,tmaptools,purrr,plotly.hrbrthemes,DT) 

#Double confirming package loading
x <- c("lubridate","data.table","zoo","riem","dplyr","tidyr","countrycode","RCurl","stringr","tidyverse","shiny","miniUI","taskscheduleR","gtrendsR","tidycensus","sf","leaflet","mapview","viridis","tidyquant","tigris","tmap","sf","maps","tidycensus","xts","ggsflabel","scales","tmaptools","purrr","plotly","hrbrthemes","DT")
lapply(x, require, character.only = TRUE)

# Load workspace with variables
load("StrykerIntelligenceWaltkthroughWorkspace.rdata")
# Get state information to loop over
stateid <- read.csv("statesid.csv");stateid <- stateid$state_id

# census key code
census_api_key("e3a3dbad3edfa4d96cb59f65931694b311565c63",install = TRUE,overwrite = TRUE)

# Census variable list
all_vars_acs5 <- load_variables(year = 2018, dataset = "acs5") # read all the variable list
all_vars_acs5

# Interactive plots
options(tigris_use_cache = TRUE)

# Remove missing values from dataframe for now
countyvariables <- na.omit(countySocialVulnerability)

```

## Census variables at the county level for the United States
Variables include: <br>
<strong> z_Poverty:</strong> z-score for percent under poverty line<br>
<strong> z_Nonwhite:</strong>  z-score for percent non-white (socially vulnerable minorities)<br>
<strong> z_Under5:</strong> z-score for percent of individuals under 5 years old (vulnerable to health issues)<br>
<strong> z_Over64: </strong>  z-score for percent of individuals over 64 years old (vulnerable to health issues)<br>
<strong> z_CoveredVulnerableAge:</strong> z-score for percent of people 5 years old or under and or 64 years old and older and have health insurance<br>
<strong> totalpopulation:</strong> total population<br>
<strong> VulIndex:</strong> People under 5, over 64, non-White and poor index<br>
<strong> PercentIncreaseInPopulation: </strong>percent increase in population from 2005-2018<br>
<strong> PercentcoveredinsuranceInvulnerableAge:</strong> Total actual number in county that is insured in vulnerable age groups<br>
<strong> TotalIncreaseInPopulation:</strong> Total actual number in county of population growth from 2005-2018<br>
<strong> PopulationToGrowthRateRatio:</strong> population divided by growth rate for 2005-2018

```{r variable,include = FALSE}
max_poverty <- max(countyvariables$z_Poverty)
min_poverty <- min(countyvariables$z_Poverty)
max_Nonwhite <- max(countyvariables$z_Nonwhite)
min_Nonwhite <- min(countyvariables$z_Nonwhite)
max_Under5 <- max(countyvariables$z_Under5)
min_Under5 <- min(countyvariables$z_Under5)
max_Over64 <- max(countyvariables$z_Over64)
min_Over64 <- min(countyvariables$z_Over64)
max_CoveredVulnerableAge <- max(countyvariables$z_CoveredVulnerableAge)
min_CoveredVulnerableAge <- min(countyvariables$z_CoveredVulnerableAge)
max_totalpopulation <- max(countyvariables$totalpopulation)
min_totalpopulation <- min(countyvariables$totalpopulation)
max_VulIndex <- max(countyvariables$VulIndex)
min_VulIndex <- min(countyvariables$VulIndex)
max_PercentIncreaseInPopulation <- max(countyvariables$PercentIncreaseInPopulation)
min_PercentIncreaseInPopulation <- min(countyvariables$PercentIncreaseInPopulation)
max_PercentcoveredinsuranceInvulnerableAge <- max(countyvariables$PercentcoveredinsuranceInvulnerableAge)
min_PercentcoveredinsuranceInvulnerableAge <- min(countyvariables$PercentcoveredinsuranceInvulnerableAge)
max_TotalIncreaseInPopulation <- max(countyvariables$TotalIncreaseInPopulation)
min_TotalIncreaseInPopulation <- min(countyvariables$TotalIncreaseInPopulation)
max_PopulationToGrowthRateRatio <- max(countyvariables$PopulationToGrowthRateRatio)
min_PopulationToGrowthRateRatio <- min(countyvariables$PopulationToGrowthRateRatio)
```

```{r datatable, echo=FALSE}
renderDT({
  datatable(countyvariables)
})
  
```

# Social Vulnerability Index 
(People of low income, 5 or below, 64 and above and non - white)

```{r columnselection, echo=FALSE}
#selectInput("SelectColumn","Select Column", choices = names(countyvariables), selected = "VulIndex" ,multiple = F)

renderLeaflet({
      m <- mapview(countyvariables, zcol = "VulIndex")
      m@map

    })


```



```{r new2,include = FALSE}
# Order by top populated columns in decending order
top_vulnerable1 <- countyvariables[order(-countyvariables$totalpopulation) , ]

# filter for variables under 98th percentile allowing for cities that are big but have room to grow
zz <- quantile(top_vulnerable1$totalpopulation, probs = c(0.98))
zz <- as.numeric(paste(zz)) # make numeric

#Only keep values under the 98th percentile 
top_vulnerable <- top_vulnerable1[top_vulnerable1$totalpopulation <= zz,]
top_vulnerable2 <- top_vulnerable[1:10,c("NAME","PercentIncreaseInPopulation")]
top_vulnerable3 <- top_vulnerable2[order(-top_vulnerable2$PercentIncreaseInPopulation),c("NAME","PercentIncreaseInPopulation")]
top_vulnerable3$PercentIncreaseInPopulation <- round(top_vulnerable3$PercentIncreaseInPopulation,digits = 3)


```

```{r new3,include= FALSE}
 p<-ggplot(data=top_vulnerable3, aes(x=reorder(NAME, -PercentIncreaseInPopulation), y=PercentIncreaseInPopulation)) +
    geom_bar(stat="identity", fill="steelblue")+
       geom_text(aes(label=PercentIncreaseInPopulation), vjust=-0.3, size=3.5)+
  theme_minimal()
Top_Growing_Metros <- p + theme(axis.text.x=element_text(angle=45, hjust=1))

```
# Hidalgo County Texas is the largest county<br> 
(Under 98th percentile for population)<br>
That also has the fastest growing population!

```{r new4}
Top_Growing_Metros
```


```{r new5,include = FALSE}
HidalgoCountyTract <- get_acs(geography = "tract"
                       , state = "TX",
                       county = "Hidalgo",
                       variables = c(totalpop2018 = "B01003_001",
                                     Totalhealthcoverage = "B27001_001",
                                     TotalcoverageMale = "B27001_002",
                                     TotalcoverageMaleUnder6 = "B27001_003",
                                     TotalcoverageMale65to74 = "B27001_024",
                                     TotalcoverageMale75andolder = "B27001_027",
                                     Totalcoveragefemale = "B27001_030",
                                     TotalcoveragefemaleUnder6 = "B27001_031",
                                     Totalcoveragefemale65to74 = "B27001_052",
                                     Totalcoveragefemale75andolder = "B27001_055"),output = "wide",geometry = TRUE)

 # Edit
HidalgoCountyTract2 <- HidalgoCountyTract %>%
   mutate(PercentcoveredinsuranceInvulnerableAge = (TotalcoverageMaleUnder6E + TotalcoverageMale65to74E + TotalcoverageMale75andolderE + TotalcoveragefemaleUnder6E + Totalcoveragefemale65to74E + Totalcoveragefemale75andolderE)/TotalhealthcoverageE) %>%
   select(NAME, GEOID,totalpop2018E,TotalhealthcoverageE, TotalcoverageMaleE,TotalcoverageMaleUnder6E,TotalcoverageMale65to74E,TotalcoverageMale75andolderE,TotalcoveragefemaleE,TotalcoveragefemaleUnder6E,Totalcoveragefemale65to74E,Totalcoveragefemale75andolderE,PercentcoveredinsuranceInvulnerableAge,TotalhealthcoverageE,geometry)
HidalgoCountyTract2$PercentcoveredinsuranceInvulnerableAge <- round(HidalgoCountyTract2$PercentcoveredinsuranceInvulnerableAge,digits = 3)
```
# Tracts in Hidalgo County <br>
Understanding the percent of people with coverage that are vulnerable <br>
(Yellow more vulnerable dark blue is less vulnerable)<br>
Tract code 4821502040 (The brightest yellow is most vulnerable population)
```{r news6}
 mapview(HidalgoCountyTract2, zcol = "PercentcoveredinsuranceInvulnerableAge", legend = FALSE)

```


```{r news7,include = FALSE}
 # Go to tract level 
 # UNIQUE MAP!!!!!!!!!!!!!!!!!
 Hidalgo_estimates <- get_estimates(geography = "county",
                              product = "characteristics",
                              breakdown = c("SEX", "AGEGROUP", "HISP","RACE"),
                              breakdown_labels = TRUE,
                              state = "TX",
                              county = "Hidalgo")

# TO GET ESTIMATES OF POPULATION CHARACTERISTICS
compare <- filter(Hidalgo_estimates, str_detect(AGEGROUP, "^Age"),
                   HISP != "Both Hispanic Origins",
                   SEX != "Both sexes") %>%
   mutate(value = ifelse(SEX == "Male", -value, value)) 

SEX <- compare$SEX
AGE <- compare$AGEGROUP
VALUE <- compare$value
RACE <- compare$RACE
# PYRIMID PLOT POPULATION FOR EACH AGE GROUP
population_by_age <- plot_ly(compare,x = VALUE, y = AGE, color  = SEX, type = 'bar', orientation = 'h',
        hoverinfo = 'y+text+name', text = VALUE) %>%
  layout(bargap = 0.1, barmode = 'overlay',
         xaxis = list(tickmode = 'array', tickvals =  c(-40000, -30000,-20000,-10000, 0,10000,20000,30000, 40000),
                      ticktext = c(-40000, -30000,-20000,-10000, 0,10000,20000,30000, 40000)))

# PYRIMID PLOT POPULATION FOR EACH AGE GROUP
population_by_race <- plot_ly(compare,x = VALUE, y = RACE, color  = SEX, type = 'bar', orientation = 'h',
        hoverinfo = 'y+text+name', text = VALUE) %>%
  layout(bargap = 0.1, barmode = 'overlay',
         xaxis = list(tickmode = 'array', tickvals =  c(-40000, -30000,-20000,-10000, 0,10000,20000,30000, 40000),
                      ticktext = c(-40000, -30000,-20000,-10000, 0,10000,20000,30000, 40000)))
####################################################
```
# Hidalgo County Demographic Makeup <br>
Population by age
```{r news8}
# PYRIMID PLOT POPULATION FOR EACH AGE GROUP
population_by_age
```
# Hidalgo County Demographic Makeup <br>
Population by race
```{r news9}
population_by_race
```

# Mobility and Covid count for the date 2020-03-23
```{r news10}

renderLeaflet({
      z <-mapview(countySocialVulnerability4, zcol="workplaces",legend= TRUE) 


      z@map

    })
```

```{r news11,include = FALSE}
# Extract covid information for Harris County USA
  install.packages("hrbrthemes",lib = "C:/R/R-4.0.2/library")
  library(hrbrthemes)
final_covid_harrison <- final_covid[final_covid$state =="Texas" & final_covid$county == "Hidalgo",]

  # Usual area chart
  p <- final_covid_harrison %>%
    ggplot( aes(x=date, y=confirmed)) +
    geom_area(fill="#69b3a2", alpha=0.5) +
    geom_line(color="#69b3a2") +
    ylab("Covid confirmed cases") +
    ggtitle("Harrison county confirmed cases") + 
    theme(plot.title = element_text(lineheight=.8, face="bold"))
    theme_ipsum()
  
  # Turn it interactive with ggplotly
  confirmed_cases <- ggplotly(p)
  
  final_mobility_harrison <- mobility2[mobility2$state =="Texas" & mobility2$county == "Hidalgo County",]

 install.packages("TSstudio",lib = "C:/R/R-4.0.2/library")
  library(TSstudio)
#  
 final_mobility_harrison2 <- final_mobility_harrison[c(6,9)]
 final_mobility_harrison2$date <- as.character(final_mobility_harrison2$date)
  final_mobility_harrison2$date <- as.POSIXct(final_mobility_harrison2$date, format="%Y-%m-%d")
final_mobility_harrison2 <- final_mobility_harrison2[order(final_mobility_harrison2$date),]


```

```{r news12}
confirmed_cases
```

 <!-- ```{r news13} -->
 <!--   #Usual area chart -->
 <!--    library(TSstudio) -->

 <!--  ts_plot(final_mobility_harrison2, -->
 <!--         title = "Hidalgo County Covid Mobility", -->
 <!--         Xtitle = "Time", -->
 <!--         Ytitle = "Percent decrease", -->
 <!--         slider = TRUE) -->

 <!-- ``` -->

# Hidalgo County Mobility
``` {r news, include = FALSE}
   library(TSstudio)

 hildalgo_mobilityz <-  ts_plot(final_mobility_harrison2,
         title = "Hidalgo County Covid Mobility",
         Xtitle = "Time",
         Ytitle = "Percent decrease",
         slider = TRUE)
```

``` {r new34}
hildalgo_mobilityz
```

# What type of instruments are Texans looking for
```{r news22, include = FALSE}
today <- Sys.time()
  ftoday <- paste(today)
  ftoday <- strsplit(ftoday," ")[[1]][1] #Split the date and get it into proper format
  var3 <- paste("2020-01-22",ftoday)
  # Can we sell them beds
  # Get information for Texas on these key words
   res2 <- gtrends(c("Hosptial beds","Surgial knives","CPR Devices"), geo = c("US-TX"),time = var3)
    res2 <- data.frame(res2$interest_over_time)  # 
```

 ```{r news30} -->
  plot(res2) -->
``` -->